An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-11 EconGrowth2.Rnw
Adjusted sizes of ternary plots.

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.75, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
standardTriPlot(data=cesTriPlotData)
@

>>>>

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
standardTriPlot(data=cesTriPlotData)
@
